The \project{unRAVE} catalog

### 2016-08-31 article/unrave.tex
Some justification of hyperparameters

\subsection{A 10-label model for detailed abundances of giant stars}
\label{sec:giant-abundance-model}

The giant stars in our training set have stellar parameters and up to 15 
individual abundances from the \apogee\ \aspcap.  Only a subset of these
elements have atomic transitions in the \rave\ wavelength region.

% The giant training set has many abundances.
% Which elements?
% Tests involving censoring? --> Just indicates that many of these lines are blended.
% So we will use regularization instead of censoring

% Set hyper-parameters by LOO-CV

% Trained this and rain it on all RAVE spectra.

@@

@@

\subsection{Internal validation}
We first conducted leave-one-out cross-validation to validate our results.
For each training set star we removed that star from the training set and
then re-trained the model.  Using that re-trained model, we then treated
the excluded star as a test star and compared our inferred labels to the
test set labels.  We show the results of this experiment in Figure
\ref{fig:loocv-comparison}.  The bias and root mean square (RMS) error in 
$\teff$ is XX~K and XX~K, and in $\logg$ is X.XX~dex and X.XX~dex,
respectively.  The bias in abundance labels is negligible --- between
X.XX to X.XX --- and the RMS varies from X.XX ([XX/H]) to X.XX ([XX/H]).
% Fill this in tomorrow.

>>>>

\subsection{A 9-label model for detailed abundances of giant stars}
\label{sec:giant-abundance-model}

The giant stars in our training set have stellar parameters and up to 15 
individual abundances from the \apogee\ \aspcap.  Only a subset of these
elements have atomic transitions in the \rave\ wavelength region: 
\ion{O}{1}, \ion{Mg}{1}, \ion{Al}{1}, \ion{Si}{1}, \ion{Ca}{2}, \ion{Ti}{1}, 
\ion{Fe}{1}, and \ion{Ni}{1}.  We excluded [Ti/H] from our abundance list 
because of systematics in the training set \citep{Holtzman_2015,Hawkins_2016}.
Therefore we are left with nine labels in our giant star model: $\teff$, 
$\logg$, and seven individual abundances.

% ARC asks: Should we discuss any tests done with censoring? 
%  			Do we feel like we need to defend our choice to use regularization
%           over censoring? The key result from the censoring tests that I did
%			is that there are a lot of atomic transitions here, but they are
% 			mostly blended. We *need* those blended lines because if you
%			censor all but the strongest line(s) for individual elements then
% 			you are left with a poor predictor of abundance labels.

We used a second-order (i.e., $\teff^2$ is the highest term) polynomial 
vectorizer for the giant star model.  We set the regularization hyperparameter
by performing a grid search of 30 $\Lambda$ points logarithmically spaced from 
$10^{-3}$ to $10^{3}$.  We performed leave-one-out cross-validation on the
training set for each value of $\Lambda$.  Specifically, we removed one star
from the training set, then trained the model, and inferred labels for the 
star that was removed from the training set.  We repeated this procedure for
every star in the training set (for every model with a different $\Lambda$)
and compared the inferred labels against the training set values.  For
comparison purposes, we also performed cross-validation on an unregularized 
($\Lambda = 0$) model using the same training set.  We calculated the bias
and root-mean-square (RMS) deviation between the input labels and those inferred
by cross-validation for every model.  The biases were negligible across all
models.  In Figure \ref{fig:giant-model-hyperparameter-search} we show the
RMS difference in label recovery compared to the unregularized model as a 
percentage improvement.  The enveloped region represents the minimum and 
maximum changes for any label with respect to the unregularized model.
Depending on the regularization strength $\Lambda$, the RMS in a given label
can decrease by $\approx30$\% with respect to the unregularized case.  At the
point of maximum improvement, near $\Lambda = X.XX$, the RMS in all labels has
decreased by at least $X$\%.  As expected the regularization produces a 
sparser matrix of $\vectheta$, with a $\approx20$\% increase in the fraction
of zero-valued entries, particularly for the cross-terms (Figure 
\ref{fig:giant-model-sparsity}, third panel).  Based on the improvement in 
RMS by cross-validation, we adopt $\Lambda = X.XX$ for our giant star model.

Results from cross-validation on our regularized model imply that the precision
in labels is XXX~K in $\teff$, X.XX~dex in $\logg$, and varies between X.XX~dex
and X.XX~dex depending on the elemental abundance.  We made no prior judgement
on whether a star was likely a giant or not; we used this model (and all other
models) to test all XXX,XXX \rave\ spectra.  Figure \ref{fig:test-set-hrd} (left
panel) shows the inferred $\teff$ and $\logg$ values for all \rave\ spectra with
S/N $\geqslant 50$.  This panel undoubtedly includes dwarf stars that cannot be
appropriately classified by our giant model.  In Section \ref{sec:joining-the-models}
we will heuristically combine these results with the main-sequence star model
described in \ref{sec:main-sequence-model}.

@@

% All them hax.

@@

Here we describe a

\subsection{Multi-epoch observations}\label{sec:repeat-observations}
